---
title: "p8105_hw5_ys3394"
author: "Yifan Su"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(ggplot2)
set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

* The raw data _Washington Post_ gatghered data mapping more than 52,000 homicides in major American cities over the past dacedes, and includes where murder is common but unsolved. 

* In the dataset, it has `r nrow(read_csv("homicide_data/homicide-data.csv"))` rows and `r ncol(read_csv("homicide_data/homicide-data.csv"))` columns. Variables in the data include characteristics of victims such as race, age and sex. Also, there are variables specify murders, including city, state they occured, and the reported date.

#### Summarize number of homicides within cities

```{r tidy_df, collapse=TRUE, message=FALSE, warning=FALSE}
# Read in the data
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

#### `prop.test` for city Baltimore

```{r baltimore, collapse=TRUE, message=FALSE, warning=FALSE}
baltimore_test =
prop.test(
  homicide_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  homicide_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>%
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

#### `prop.test` for each of the cities

```{r cities, collapse=TRUE, message=FALSE, warning=FALSE}
results_df = 
  homicide_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

#### A plot showing estimates and CIs for each city

```{r bar_plot, collapse=TRUE, message=FALSE, warning=FALSE}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(y = city_state, x = estimate)) +
  geom_point() + 
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  labs(x = "Estimated proportion",
       y = "City",
       title = "Estimates and CIs for each city")
```


## Problem 2 ideas ...


import one dataset 

```{r}
data_1 = read_csv("lda_data/con_01.csv")
```

```{r, error = TRUE}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x)),
    arm_id = str_remove(path, "lda_data/"),
    arm_id = str_remove(arm_id, ".csv")) %>% 
  unnest(data) %>% 
  select(-path) %>% 
  pivot_longer(
    week_1:week_8,
    values_to = "arm_data",
    names_to = "week"
  ) %>% 
  separate(arm_id, into = c("arm", "id"), sep = "_")
  
```



```{r}
plot_spaghetti =
  path_df %>% 
  unite("arm_id", arm:id, remove = FALSE) %>% 
  ggplot(aes(x = week, y = arm_data, group = arm_id, color = arm)) +
  geom_point() +
  geom_line() +
  labs(x = "Week",
       y = "Measurement for two arms",
       title = "Observations in two arms over 8 weeks")
```


## Problem 3

```{r}
n = 30
mu = 5
sigma = 5
x = rnorm(n, mean = mu, sd = sigma)
t.test(x, mu = mu, conf.level = 0.95)
```

